---
title: "My shiny App presentation"
author: "AbdulAziz Ascandari"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This app is firstly about the finishing of the Coursera Course Developing Data products. 
The second focus lies on to develop a basic tooling to generate pseudo-random numbers.

First you type, ore slide, the desired number a random numbers (between 0 and 1337).
With the next two sliders you can adjust the minimum and maximum number of x and y axis.
This indicates the boundries within the numbers selected at first are sampled.

If the conditions are satisfactory then you can click on "press please" button.
You can find all code in on Github.

***

## The UI code

```{r}
library(markdown)
library(shiny)

shinyUI(navbarPage("Random number generator",
                   tabPanel("Random numbers",
                            
                            sidebarLayout(
                              sidebarPanel(
                                helpText("Give the number of random numbers to be plotted and adjust the axis "),
                                numericInput("numeric", "How many random numbers should be plotted?",
                                             value = 1337, min = 0, max = 1337, step = 1),
                                sliderInput("xslider", "Pick a minimum and maximum number for the x-axis between -1337 and 1337 if you like",
                                            -1337, 1337, value = c(-137, 137)),
                                sliderInput("yslider", "Pick a minimum and maximum number for the y-axis between -1337 and 1337 if you like",
                                            -1337, 1337, value = c(-137, 137)),
                                submitButton("Press please")
                              ),
                              
                              mainPanel(
                                h4("Your own random generated numbers"),
                                plotOutput("plot1")
                              )
                            )
                   ),
                   
                   tabPanel("About random numbers",
                            mainPanel(
                              includeMarkdown("about")
                            )) 
) 
) 
```

## The Server code

```{r}
library(markdown)
library(shiny)
shinyServer(function(input, output) {
  output$plot1 <- renderPlot({ par(bg = "lightblue", fg = "blue", col = "red")
    set.seed(1337)
    numberpoints <- input$numeric
    minx <- input$xslider[1]
    maxx <- input$xslider[2]
    miny <- input$yslider[1]
    maxy <- input$yslider[2]
    datax <- runif(numberpoints, minx, maxx)
    datay <- runif(numberpoints, miny, maxy)
    plot(datax, datay, xlab = " random number on x axis", ylab = " random number on y axis", main = "Random numbers generated",
         xlim = c(-1337, 1337), ylim = c(-1337, 1337))
  })
  
}) 
```

# Where to find the files to the app
Find the files to the app here : https://github.com/AscanOfficiel2/Shiny_app.git